Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-05-11 manuscript-figures.Rmd
Update manuscript-figures.Rmd

data.R0_norm <- data.R0 %>% 
  filter(KH %in% newKH_vals) %>% 
  filter(variable == "R0") %>%
  select(-variable) %>%
  # normalize variables to have a maximum of 1
  group_by(system_ID, Model, sigmaH, KH) %>% 
  # mutate(mean_norm = mean / max(mean)) %>% 
  mutate(median_norm = median / max(median)) %>%
  # mutate(highHCI_norm = highHCI / max(median)) %>% 
  # mutate(lowHCI_norm = lowHCI / max(median)) %>% 
  arrange(system_ID, sigmaH, KH, Temperature, mean_norm)

>>>>

data.R0_norm <- data.R0 %>% 
  filter(KH %in% newKH_vals) %>% 
  filter(variable == "R0") %>%
  select(-variable) %>%
  # normalize variables to have a maximum of 1
  group_by(system_ID, Model, sigmaH, KH) %>% 
  # mutate(mean_norm = mean / max(mean)) %>% 
  mutate(median_norm = median / max(median)) %>%
  # mutate(highHCI_norm = highHCI / max(median)) %>% 
  # mutate(lowHCI_norm = lowHCI / max(median)) %>% 
  arrange(system_ID, sigmaH, KH, Temperature, median_norm)
